### 2021-05-14 Modules/arrayPerformance_beamwidth_LOCAL.tex
Acronyms added

% The half power beamwidth (HPBW), denoted as $\dThetaHPBW$ quantifies the array's main lobe narrowness.
% It represents the DOA where the beampattern's energy reduces to half of its maximal value.
\par In App.~\ref{apdx_HPBW} we extend the known result of \eqref{eq_known_HBPW} for any $r\geq 0$. It turns out that for large $N$, the HPBW is obtained by solving for $x$ the equality
\begin{equation}\label{eq_HPBW}
    % \resizebox{1\linewidth}{!}{
        \begin{split}
            \rBrace{r^{2}-4r+2}\frac{\sin{\rBrace{x}}^{2}}{x^{2}}+r\frac{\sin{\rBrace{2x}}}{x}-1=0
        \end{split}
    % }
\end{equation}
where we define $x\triangleq{} N\dTheta_{HPBW}/2$. In Fig.~\ref{fig_feedbackULA_HPBW_Nx_vs_N_variousR} we plot the numerical solution of \eqref{eq_HPBW} for various values of $r$ and $N$, showing that $x$ reaches its limit around $N=20$. Also note that for $r=0$ we obtain the known result of standard ULA with the limiting factor of $1.4$.
Having the limiting factors for various values of the gain mismatch $r$, we investigate the feedback related improvement and express the HPBW by
\[
\dThetaHPBW/2\approx \frac{1.4}{f(r)N}.
\]
Note that $f(r)$ represents the array aperture improvement factor, compared to the standard ULA.
To find a suitable expression for $f\rBrace{r}$, we computed $\Hr_{\Delta\theta,\Delta\phi=0,r}$ using $N=100$ on a fine grid of $r$ values (actually slicing a vertical column of Fig.~\ref{fig_feedbackULA_HPBW_Nx_vs_N_variousR} at $N=100$) and looked for proper polynomial approximation (using MATLAB\textsuperscript{\textregistered}) for the HPBW.
It turns out that the 2-nd order polynomial fit satisfies
\begin{equation}
    \label{eq_Bapprox}
    f\rBrace{r}\approx\frac{1.4}{\rBrace{1-r}\rBrace{-0.4r+1.4}}.
\end{equation}
Note that for an accurate gain match (i.e., $r\to1$), the RHS of \eqref{eq_Bapprox} tends towards infinity, implying that the equivalent array has an infinite number  of elements ($f\rBrace{r}N$), hence obtaining perfect spatial selectivity.
\begin{figure}[t]
    \begin{center}
        \begin{overpic}[width=0.65\linewidth, 
        %grid, 
        tics=10,trim=0 0 0 0]{./Media/spatial_IIR_MATLAB/arrayParameters/HPBW_vs_N_various_r.eps}
            \put (4, 75){\footnotesize{$N\dThetaHPBW/2$}}
            \put (50, 62.5) {\footnotesize{$r=0$}}
            \put (50, 54) {\footnotesize{$r=0.1$}}
            \put (50, 39.5) {\footnotesize{$r=0.3$}}
            \put (50, 28.5) {\footnotesize{$r=0.5$}}
            \put (50, 19.75) {\footnotesize{$r=0.7$}}
            \put (50, 12.5) {\footnotesize{$r=0.9$}}
            \put (50, 2) {\footnotesize{$N$}}
        \end{overpic}
    \end{center}
     \caption{Plot of $x=N\dThetaHPBW/2$ vs. $N$, for various $r$ values, obtained by numerically solving \eqref{eq_HPBW}.}
    \label{fig_feedbackULA_HPBW_Nx_vs_N_variousR}
\end{figure}
\begin{figure}[t]
    \begin{center}
        \begin{overpic}[width=0.65\linewidth, 
        % grid, 
        tics=10,trim=0 0 0 0]{./Media/HPBW_limit_vs_r.eps}
            \put (39.5, 63.5) {\scriptsize{Numerical solution of \eqref{eq_HPBW}}}
            \put (39.5, 58.25) {\scriptsize{Polynomial fitting \eqref{eq_Bapprox}}}
            \put (39.5, 52.5) {\footnotesize{$\log_{10}f\rBrace{r}$}}
            \put (85, 75) {\footnotesize{$\log_{10}f\rBrace{r}$}}
            \put (4, 75){\footnotesize{$N\dThetaHPBW/2$}}
            \put (50, 2) {\footnotesize{$r$}}
        \end{overpic}
    \end{center}
    \caption{Evaluation of $N\dThetaHPBW/2$ for $N=100$ and its approximation $1.4/f\rBrace{r}$  (marked by red diamonds). $f\rBrace{r}$ is also presented, in logarithmic scale (dotted curve).} 
    \label{fig_feedbackULA_beamwidth_limit_r_dependent}
\end{figure}

>>>>

% The half power beamwidth (HPBW), denoted as $\dThetaHPBW$ quantifies the array's main lobe narrowness.
% It represents the DOA where the beampattern's energy reduces to half of its maximal value.
\par In App.~\ref{apdx_HPBW} we extend the known result of \eqref{eq_known_HBPW} for any $r\geq 0$. It turns out that for large $N$, the HPBW is obtained by solving for $x$ the equality
\begin{equation}\label{eq_HPBW}
    % \resizebox{1\linewidth}{!}{
        \begin{split}
            \rBrace{r^{2}-4r+2}\frac{\sin{\rBrace{x}}^{2}}{x^{2}}+r\frac{\sin{\rBrace{2x}}}{x}-1=0
        \end{split}
    % }
\end{equation}
where we define $x\triangleq{} N\dTheta_{HPBW}/2$. In Fig.~\ref{fig_feedbackULA_HPBW_Nx_vs_N_variousR} we plot the numerical solution of \eqref{eq_HPBW} for various values of $r$ and $N$, showing that $x$ reaches its limit around $N=20$. Also note that for $r=0$ we obtain the known result of standard ULA with the limiting factor of $1.4$.
Having the limiting factors for various values of the gain mismatch $r$, we investigate the feedback related improvement and express the HPBW by
\[
\dThetaHPBW/2\approx \frac{1.4}{f(r)N}.
\]
Note that $f(r)$ represents the array aperture improvement factor, compared to the standard ULA.
To find a suitable expression for $f\rBrace{r}$, we computed $\Hr_{\Delta\theta,\Delta\phi=0,r}$ using $N=100$ on a fine grid of $r$ values and looked for proper polynomial approximation (using MATLAB\textsuperscript{\textregistered}) for the HPBW.
It turns out that the 2-nd order polynomial fit satisfies
\begin{equation}
    \label{eq_Bapprox}
    f\rBrace{r}\approx\frac{1.4}{\rBrace{1-r}\rBrace{-0.4r+1.4}}.
\end{equation}
Note that for an accurate gain match (i.e., $r\to1$), the RHS of \eqref{eq_Bapprox} tends towards infinity, implying that the equivalent array has an infinite number  of elements ($f\rBrace{r}N$), hence obtaining perfect spatial selectivity (see Fig.~\ref{fig_feedbackULA_beamwidth_limit_r_dependent}).
\begin{figure}[t]
    \begin{center}
        \begin{overpic}[width=0.65\linewidth, 
        %grid, 
        tics=10,trim=0 0 0 0]{./Media/spatial_IIR_MATLAB/arrayParameters/HPBW_vs_N_various_r.eps}
            \put (4, 75){\footnotesize{$N\dThetaHPBW/2$}}
            \put (50, 62.5) {\footnotesize{$r=0$}}
            \put (50, 54) {\footnotesize{$r=0.1$}}
            \put (50, 39.5) {\footnotesize{$r=0.3$}}
            \put (50, 28.5) {\footnotesize{$r=0.5$}}
            \put (50, 19.75) {\footnotesize{$r=0.7$}}
            \put (50, 12.5) {\footnotesize{$r=0.9$}}
            \put (50, 2) {\footnotesize{$N$}}
        \end{overpic}
    \end{center}
     \caption{Plot of $x=N\dThetaHPBW/2$ vs. $N$, for various $r$ values, obtained by numerically solving \eqref{eq_HPBW}.}
    \label{fig_feedbackULA_HPBW_Nx_vs_N_variousR}
\end{figure}
\begin{figure}[t]
    \begin{center}
        \begin{overpic}[width=0.65\linewidth, 
        % grid, 
        tics=10,trim=0 0 0 0]{./Media/HPBW_limit_vs_r.eps}
            \put (39.5, 63.5) {\scriptsize{Numerical solution of \eqref{eq_HPBW}}}
            \put (39.5, 58.25) {\scriptsize{Polynomial fitting \eqref{eq_Bapprox}}}
            \put (39.5, 52.5) {\footnotesize{$\log_{10}f\rBrace{r}$}}
            \put (85, 75) {\footnotesize{$\log_{10}f\rBrace{r}$}}
            \put (4, 75){\footnotesize{$N\dThetaHPBW/2$}}
            \put (50, 2) {\footnotesize{$r$}}
        \end{overpic}
    \end{center}
    \caption{Evaluation of $N\dThetaHPBW/2$ for $N=100$ and its approximation $1.4/f\rBrace{r}$  (marked by red diamonds). $f\rBrace{r}$ is also presented, in logarithmic scale (dotted curve).} 
    \label{fig_feedbackULA_beamwidth_limit_r_dependent}
\end{figure}

### 2021-05-14 Modules/paper_sec_prlms.tex
After Israel's comments
Acronyms added

In this chapter, we revisit the most basic DOA estimation approach, i.e. beamforming, and present our novel feedback based architecture.
The feedback based beamforming concept is introduced in Sec.~\ref{sec_introduceFeedback}.
Then, we apply information theory related reasoning for the array setting in Sec.~\ref{sec_FIM}, namely we use the Fisher Information Matrix (FIM).
The resultant beamformer's temporal response and spatial performance are analysed in Sec.~\ref{sec_stability} and Sec.~\ref{sec_Performance} respectively, assuming ideal noiseless scenario.
Considering noisy setups, the beamformer's noise sensitivity is exemplified in Sec.\ref{sec_sim}, followed by a practical and robust dual-frequency beamformer which is presented in Sec.~\ref{sec_app}.

@@

The suggested feedback beamformer (FB) architecture, where the output signal ($z$) is synthesized using weights $\vBeta$ and the weights $\vAlpha$ synthesize the feedback transmission ($\Tx$), is presented in Fig.~\ref{fig:Proposed_spatialIIR_ARCH}. The beamformer's output and the feedback signal are synthesized using two independently configured beamformers, $s$ is the system's stimulus and an additive noise (n) is assumed at the array's output.

@@

Note that setting $\vAlpha=\vecnot{0}$ (i.e., cancelling the feedback) degenerates the system to a plain delay-and-sum (DS) beamformer.

@@

    The proposed feedback beamformer.

@@

    We designate the feedback beamformer block (dashed line) for later use.

@@

In this section we analyze the suggested FB (see Fig.~\ref{fig:Proposed_spatialIIR_ARCH}), considering some fundamental properties which are commonly used to asses array performance and discussed in Sec.~\ref{sec:prlm_array_perf}: Beamwidth, peak-to-sidelobe level, and directivity. Each property is then compared to traditional passive ULAs, showing that significantly improved performances are obtainable with spatial feedback integration.

@@

Applying the \emph{normalized beampattern} concept of Sec.~\ref{sec:prlm_array_perf} to this work, we set $\vecnot{\beta}_{\coefSetName,\text{opt}}=\vecnot{\alpha}_{\coefSetName,\text{opt}},$ giving rise to

@@

        H_{\vecnot{\beta}_{\coefSetName,\text{opt}},\vecnot{\alpha}_{\coefSetName,\text{opt}}}

@@

        \frac{\rBrace{1-r}\D{\dTheta/2}{N}}{\exp\rBrace{j\rBrace{\dPhi+(N-1)\dTheta/2}}-r\D{\dTheta/2}{N}}.

@@

             \frac{\rBrace{1-r}\D{\dTheta/2}{N}}{\exp\rBrace{j\rBrace{(N-1)\dTheta/2}}-r\D{\dTheta/2}{N}},

@@

@@

        \begin{overpic}[width=0.75\linewidth, 

@@

@@

@@

As the expressions for HPBW and sidelobe-attenuation are relevant for $\sim{}N>20$, we also simulate 20 elements ULA for in Fig.~\ref{fig_perf20}. 

@@

     \caption{Simulating 3 elements ULA based feedback beamformer for $r$ values of 0, 0.3, 0.6 and 0.8.

@@

    \caption{Performances of conventional beamformer $r=0$ and the proposed Feedback-Beamforming Architecture, for several $r$ values.

>>>>

In this chapter, we revisit the most basic DOA estimation approach, i.e. beamforming, and present our novel feedback based architecture.
The feedback based beamforming concept is elaborated in Sec.~\ref{sec_introduceFeedback}.
Then, we apply information theory related reasoning for the array setting in Sec.~\ref{sec_FIM}, namely we use the FIM to design the coefficients of the suggested beamformer.
The resultant beamformer's temporal response and spatial performance are analysed in Sec.~\ref{sec_stability} and Sec.~\ref{sec_Performance} respectively, assuming ideal noiseless scenario.
Considering noisy setups, the beamformer's noise sensitivity is exemplified in Sec.~\ref{sec_sim}, followed by a practical and robust dual-frequency beamformer design which is presented in Sec.~\ref{sec_app}.

@@

The suggested FB architecture, where the output signal ($z$) is synthesized using weights $\vBeta$ and the weights $\vAlpha$ synthesize the feedback transmission ($\Tx$), is presented in Fig.~\ref{fig:Proposed_spatialIIR_ARCH}. The beamformer's output and the feedback signal are synthesized using two independently configured beamformers, $s$ is the system's stimulus and an additive noise (n) is assumed at the array's output.

@@

Note that setting $\vAlpha=\vecnot{0}$ (i.e., cancelling the feedback) degenerates the system to the convectional beamformer (CB) beamformer.

@@

    The proposed FB.

@@

    We designate the FB block (dashed line) for later use.

@@

In this section we analyze the suggested FB (see Fig.~\ref{fig:Proposed_spatialIIR_ARCH}), considering some fundamental properties which are commonly used to asses array performance and were discussed in Sec.~\ref{sec:prlm_array_perf}: Beamwidth, peak-to-sidelobe level, and directivity. Each property is then compared to traditional passive ULAs, showing that significantly improved performances are obtainable with spatial feedback integration.

@@

Applying the \emph{normalized beampattern} notation of Sec.~\ref{sec:prlm_array_perf}, we set $\vecnot{\beta}_{\coefSetName}=\vecnot{\alpha}_{\coefSetName}.$ 
Considering the unavoidable errors mentioned in \ref{subsec_error_trms} (i.e. $\Delta\theta, \Delta\phi$ and $r$), we define $\HrTPr$ as the general scenario normalized array response.
We choose to normalize the spatial response according to $H_{0}$ (of \eqref{eq:SF_CB_gainMismatch}), giving rise to

@@

        H_{0}

@@

        \frac{\rBrace{1-r}\D{\dTheta/2}{N}}{\exp\cBrace{j\vBrace{\dPhi+\rBrace{N-1}\dTheta/2}}-r\D{\dTheta/2}{N}}.

@@

             \frac{\rBrace{1-r}\D{\dTheta/2}{N}}{\exp\cBrace{j\vBrace{\rBrace{N-1}\dTheta/2}}-r\D{\dTheta/2}{N}},

@@

\begin{figure}
    \begin{minipage}{0.45\textwidth}

@@

            \begin{overpic}[width=\linewidth, 

@@

    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
            \begin{overpic}[width=\linewidth, 
                tics=10,trim=0 0 0 0]{./Media/directivityErr.png}
                    \put (18, 6){\footnotesize{$N$}}
                    \put (72, 3){\footnotesize{$r$}}
                    \put (0, 68){\footnotesize{Error}}
        \caption{The error between numerical calculation and the analytic expression.}
        \label{fig_directivityErr}

@@

% \begin{figure}[t]
%     \begin{center}
%         \begin{overpic}[width=0.75\linewidth, 
%         %grid, 
%         tics=10,trim=0 0 0 0]{./Media/directivity_expr.eps}
%             \put (20, 10){\footnotesize{$N$}}
%             \put (72, 6){\footnotesize{$r$}}
%             \put (16.5, 70){\footnotesize{Numerical integration}}
%             \put (16.5, 65){\footnotesize{$\rBrace{N-r}/\rBrace{1-r}$}}
%             \put (-9, 45){\footnotesize{$\mathcal{D}\rBrace{N,r}$}}
%         \end{overpic}
%     \end{center}
%      \caption{Plot of $\mathcal{D}\rBrace{N,r}$, computed using numerical integration (surface), shown to perfectly match the analytic expression (black diamonds) presented in \eqref{eq_D_result}.}
%     \label{fig_directivity}
% \end{figure}

@@

As the expressions for HPBW and sidelobe-attenuation are relevant for $\sim{}N>20$, we also simulate 20 elements ULA in Fig.~\ref{fig_perf20}. 

@@

     \caption{Simulating 3 elements ULA based FB for $r$ values of 0, 0.3, 0.6 and 0.8.

@@

    \caption{Performances of CB $r=0$ and the proposed Feedback-Beamforming Architecture, for several $r$ values.

### 2021-05-14 Modules/sec_FIM_and_CRLB.tex
Acronyms added

Considering narrowband signals, this choice of weights may be interpreted as a generalized version of the \emph{conventional beamformer} (CB) \cite{van2004optimum} which is a mere time shift (phase shift in narrowband signals) of the input signals as if the impinging wave is coming from the array's boresight direction (i.e. $\theta_{d}=\pi/2$) as illustrated in Fig.\ref{fig_CB_vanTrees}.

@@

    The \emph{conventional beamformer} - time shifting the input signals as if the impinging wave from a certain DOA arrives from the array's boresight.

>>>>

Considering narrowband signals, this choice of weights may be interpreted as a generalized version of the CB \cite{van2004optimum} which is a mere coherent summation of the feedback signal.

@@

    The CB - time shifting the input signals as if the impinging wave from a certain DOA arrives from the array's boresight.

### 2021-05-14 Modules/sec_conclusions_LOCAL.tex
rev03
Acronyms added

Integrating feedback into standard beamformers proved to achieve the spatial domain equivalent of the temporal IIR filtering.
It seems that a simple generalization of the conventional-beamformer maximizes (locally) the system's spatial information, thus enabling high localization accuracy.
The feedback-based architecture performance evaluation predicts an unlimited improvement in all criteria, when considering perfect knowledge of the target's range and the channel attenuation.
It turns out that a single frequency waveform based feedback-beamformer is impractical, being too sensitive to even mild target range estimation errors.
Fortunately, using a dual-frequency waveform and applying simple frequency domain manipulations to the output and feedback signals, were found to serve as a low frequency (hence low sensitivity) equivalent of the single frequency scheme.
Also, the dual frequency scheme proved to be of low noise sensitivity, featuring high performance even in relatively low signal-to-noise-ratio scenarios.
\par In the following, we overview some interesting leads for future study of the feedback beamforming concept.

>>>>

In this work we have suggested a novel approach to beamforming and localization, which is based on a generating a continuous feedback between the array and the target of interest.
Integrating feedback into standard beamformers proved to achieve the spatial domain equivalent of the temporal IIR filtering.
It seems that a simple generalization of the conventional-beamformer maximizes (locally) the system's spatial information, thus enabling high localization accuracy.
The feedback-based architecture performance evaluation predicts an unlimited improvement in all criteria, when considering perfect knowledge of the target's range and the channel attenuation.
It turns out that a single frequency waveform based feedback-beamformer is impractical, being too sensitive to even mild target range estimation errors.
Fortunately, using a DF waveform and applying simple frequency domain manipulations to the output and feedback signals, were found to serve as a low frequency (hence low sensitivity) equivalent of the single frequency scheme.
Also, the DF scheme proved to be of low noise sensitivity, featuring high performance even in relatively low signal-to-noise-ratio scenarios.
\par In the following, we overview some interesting leads for future study of the FB concept.

### 2021-05-14 Modules/sec_future_coef.tex
Sent as draft No.2
rev03
Acronyms added

As mentioned in Sec.~\ref{sec_introduceFeedback}, the reasoning for the selection of $\vecnot{\alpha}, \vecnot{\beta}$ as the conventional beamformer generalization, was the FIM related information considerations.
Obviously, there are many more possibilities/considerations to choosing the coefficient.
Some examples for such coefficient choosing schemes may include
\begin{itemize}
    \item Finite word affects
    \item Nulling of specific DOAs
    \item Setting all poles in a single DOA may lead to enhanced directivity
    \item General radiation patterns of the sensors
\end{itemize}
and many more.

>>>>

As mentioned in Sec.~\ref{sec_introduceFeedback}, the reasoning for the selection of $\vecnot{\alpha}, \vecnot{\beta}$ as the CB generalization, was the FIM related information considerations.
Obviously, there are many more possibilities/considerations to choosing the coefficient.
Some examples for such coefficient choosing schemes may include
\begin{itemize}
    \item Finite word effects
    \item Nulling of specific DOAs \\
    For example, it is interesting to see the FB equivalent to Capon's \cite{capon1969high} MVDR. 
\end{itemize}
and many more.

### 2021-05-14 Modules/sec_future_dynamic.tex
After Israel's comments
Acronyms added

Revisiting \eqref{eqn:SingleSensorTemporalEquality}, a natural initial generalization would be to allow the target of interest to be dynamic, i.e. introducing a general 3D arbitrary target location $\vecnot{p}_{t}\rBrace{t}$.
The location dynamics may be represented in terms of dynamic propagation delay, $\tau_{pd}\rBrace{t}$ and Doppler.
It follows that an auxiliary temporal quantity should be defined, which for a given impinging signal, expresses it's transmission time. 
Hence, we denote the moment of transmission $t_{i}\rBrace{t}$ as
\begin{equation}
\label{eq_fut_dyn_ti}
    t_{i}\rBrace{t} = \cBrace{t - 2\tau\ \middle\vert\ \tau = \frac{R\rBrace{t-\tau}}{c}}
\end{equation}
With $t_{i}$, we rewrite \eqref{eqn:SingleSensorTemporalEquality} as
\begin{equation}
    \label{eq_fut_dyn_temp}
    x_{n}(t) = g\rBrace{s\rBrace{t_{i}\rBrace{t}}
    +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{t_{i}\rBrace{t}}}}.
\end{equation}
For example, consider a target with constant, radial only (constant DOA) velocity $v$ with respect to the array which is initially positioned with distance of $R_{0}$ from the array.
It follows that
\begin{equation}
    \label{eq_fut_constV_Rt}
    R\rBrace{t} = R_{0} + vt
\end{equation}
which when plugged into \eqref{eq_fut_dyn_ti} gives rise to
\begin{equation}
    \label{eq_fut_constV_ti}
    t_{i}\rBrace{t}=\frac{c-v}{c+v}t-\frac{2R_{0}}{c+v}
\end{equation}
and it follows that
\begin{equation}
    \label{eq_fut_constV_xn}
    x_{n}(t) = g\rBrace{s\rBrace{\frac{c-v}{c+v}t-\frac{2R_{0}}{c+v}}
    +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{\frac{c-v}{c+v}t-\frac{2R_{0}}{c+v}}}}.
\end{equation}
Then, similar steps as in Sec.~\ref{sec_introduceFeedback} are to be made to get an expression for the system's response $H$.
It is expected that as in RADAR systems, the tracking of the object should now also take Doppler shifts as the returning signal is frequency shifted.
% One may consider the following research approaches for further investigation
% \begin{itemize}
%     \item \textbf{Modeling of target's location}
%     \\Considering a constant velocity $\vecnot{v}_{\theta,\phi}$, of the target, where $v_{\theta}$ and $v_{\phi}$ are the radial and the tangent velocity components respectively, will result in a closed form expression for $t_{i}$, $$t_{i}=\frac{R\rBrace{t=0}+\rBrace{c+v_{\theta}}t}{c},$$ where $R\rBrace{t=0}$ is the initial distance to the target of interest and further development may lead to a closed form response like in the stationary case.
%     In this manner, other components may be added to the positional equation.
%     \item \textbf{Frame based processing}
%     \\Considering low velocity of the target with respect to the wave's propagation's speed, one may consider treating the processor as pseudo-stationary and explore its implications for increasing velocities/processing duration. 
% \end{itemize}

>>>>

Revisiting \eqref{eqn:SingleSensorTemporalEquality}, a natural initial generalization would be to allow the target of interest to be dynamic, i.e. introducing a general 3D arbitrary target location $\vecnot{p}_{t}\rBrace{t}$.
The location dynamics may be represented in terms of dynamic propagation delay, $\tau_{pd}\rBrace{t}$ and Doppler.
% It follows that an auxiliary temporal quantity should be defined, which for a given impinging signal, expresses it's transmission time.
\par
Following the basic steps of temporal analysis, as in Chapter.~\ref{chap:firstchap}, starts with expressing the impinging signal of a single sensor.
As in the analysis of static target scenario, the signal consists of two contributions, i.e. the reflected emitted signal and the reflected feedback signal.
Therefore, for each moment $t$, we should resolve the corresponding moment in which the current impinging signals were emitted by the array.
\par
To this end, we first denote $t_{\text{ref}}\rBrace{t}$ the moment in which the currently impinging signal was reflected by the target of interest.
Another auxiliary quantity is reflection moment's corresponding target range $\tau_{\text{ref}}$ where the following relation holds
\begin{equation}
\label{eq_tRef_relation}
    t-\frac{R\rBrace{t_{\text{ref}}\rBrace{t}}}{c} = t_{\text{ref}}\rBrace{t}.
\end{equation}
Assuming $t_{\text{ref}}\rBrace{t}$ is resolved, we denote the propagation delay at the reflection moment $\tau_{\text{ref}}\rBrace{t} = R\rBrace{t_{\text{ref}}\rBrace{t}}/c$ and express the emission moment as
\begin{equation}
\label{eq_tTX}
    t_{\text{\tiny{TX}}}\rBrace{t} 
    = 
    t_{\text{ref}}\rBrace{t} - \tau_{\text{ref}}\rBrace{t} 
    =
    t - 2\tau_{\text{ref}}\rBrace{t}.
\end{equation}
With $t_{\text{\tiny{TX}}}$, we rewrite \eqref{eqn:SingleSensorTemporalEquality} as
\begin{equation}
    \label{eq_fut_dyn_temp}
    x_{n}(t) = g\rBrace{s\rBrace{t_{\text{\tiny{TX}}}\rBrace{t}}
    +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{t_{\text{\tiny{TX}}}\rBrace{t}}}}.
\end{equation}
\par
Obviously, to have a closed form expression for $x_{n}(t)$, there should be a model for the target's dynamics (i.e. $\vpt{}$).
Such an example, is a target with constant radial (constant DOA) velocity $v$ with respect to the array which is initially positioned with distance of $R_{0}$ from the array.
It follows that
\begin{equation}
    \label{eq_fut_constV_Rt}
    R\rBrace{t} = R_{0} + vt
\end{equation}
which when plugged into \eqref{eq_tRef_relation} gives rise to
\begin{equation}
    \label{eq_fut_constV_ti}
    t_{\text{\tiny{TX}}}\rBrace{t}=\frac{c-v}{c+v}t-\frac{2R_{0}}{c+v}
\end{equation}
and it follows that
\begin{equation}
    \label{eq_fut_constV_xn}
    x_{n}(t) = g\vBrace{s\rBrace{\frac{c-v}{c+v}t-\frac{2R_{0}}{c+v}}
    +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{\frac{c-v}{c+v}t-\frac{2R_{0}}{c+v}}}}.
\end{equation}
Then, similar steps as in Sec.~\ref{sec_introduceFeedback} are to be made to get an expression for the system's response $H$.
It is expected that as in RADAR systems, the tracking of the object should now also take Doppler shifts into account.
% One may consider the following research approaches for further investigation
% \begin{itemize}
%     \item \textbf{Modeling of target's location}
%     \\Considering a constant velocity $\vecnot{v}_{\theta,\phi}$, of the target, where $v_{\theta}$ and $v_{\phi}$ are the radial and the tangent velocity components respectively, will result in a closed form expression for $t_{\text{\tiny{TX}}}$, $$t_{\text{\tiny{TX}}}=\frac{R\rBrace{t=0}+\rBrace{c+v_{\theta}}t}{c},$$ where $R\rBrace{t=0}$ is the initial distance to the target of interest and further development may lead to a closed form response like in the stationary case.
%     In this manner, other components may be added to the positional equation.
%     \item \textbf{Frame based processing}
%     \\Considering low velocity of the target with respect to the wave's propagation's speed, one may consider treating the processor as pseudo-stationary and explore its implications for increasing velocities/processing duration. 
% \end{itemize}

### 2021-05-14 Modules/sec_future_multiTarget.tex
Acronyms added

Considering practical scenarios of multiple ($P$) targets, positioned in $p_{t_,i}\ \forall i\in0\dots{}P-1$, the obvious expansion of \eqref{eqn:SingleSensorTemporalEquality} is 
\begin{equation}
    \label{eqn:ftr_dyn_temp}
    x_{n}(t) = \sum_{i=0}^{i=P-1}{\vBrace{g\rBrace{s\rBrace{t-\tau_{pd,i}-\tau_{n,i}}
    +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{t-\tau_{pd,i}-\tau_{n,i}}}}}},
\end{equation}
where $\tau_{pd,i}$ is the delay of the signal which reflected from $p_{t,i}$.
Interesting directions of research may include
\begin{itemize}
    \item The affects of closely positioned targets
    \item Localization resolution
    \item Maximal number of simultaneously detected targets with respect to N
    \item Independent beamforming per target with multiple transmitters steering the feedback signal. 
\end{itemize}

>>>>

Considering practical scenarios of multiple ($P$) targets, positioned in $p_{t_,i}\ \forall i\in0\dots{}P-1$, the obvious generalization of \eqref{eqn:SingleSensorTemporalEquality} is 
\begin{equation}
    \label{eqn:ftr_dyn_temp}
    x_{n}(t) = \sum_{i=0}^{i=P-1}{\vBrace{g\rBrace{s\rBrace{t-\tau_{pd,i}-\tau_{n,i}}
    +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{t-\tau_{pd,i}-\tau_{n,i}}}}}},
\end{equation}
where $\tau_{pd,i}$ is the delay of the signal which reflected from $p_{t,i}$.
Interesting directions of research may include
\begin{itemize}
    \item The effects of closely positioned targets
    \item Localization resolution
    \item Maximal number of simultaneously detected targets with respect to N
    \item Independent beamforming per target with multiple transmitters steering the feedback signal. 
\end{itemize}

### 2021-05-14 Modules/sec_future_wavfrom.tex
Acronyms added

In practical RADAR related systems, the waveform of choice is pulse (in most cases, chirp) based.
It holds some obvious advantages over the CW transmission such as
\begin{itemize}
    \item Lower power consumption due to lower transmissions duty cycle. 
    \item In multi target scenario, there is a smaller chance of interference for the reflected signals from the targets temporally distinct if the targets are in different distances.
    \item The use of wide band signals may as in RADAR systems, increase spatial resolution in the radial axis.
\end{itemize}
Another interesting option is the using several (possibly many) independent harmonics as super positioned multiple dual frequency beamformers, which simultaneously scan a wide area with multiple resolutions.
By merely selecting harmonic couples and filter coefficients, each harmonics pair is pointed to a specific area.
It follows that with the expense of computational effort (without adding elements to the array), it seems possible that one may have simultaneous scan of the entire arena in any wanted direction/range/resolution.
\par 
As a simple example, consider that the arena consists of $M$ zones of interest, where each zone may be described as a angular bounded radial slice (similar to the visualization of Fig.~\ref{fig_rangeAzimuthSelectivity}) which may be described as $$a_{m}=\cBrace{\vecnot{p}\ \middle\vert\  \theta_{d,m,\text{min}}<\text{DOA}\rBrace{\vecnot{p}}<\theta_{d,m,\text{max}}\ ,\ R_{m,\text{min}}<\norm{\vecnot{p}}<R_{m,\text{max}}}\ \forall\ m=0\dots{}M-1.$$
\par
Each zone will be assigned with matching couple of carrier frequencies ($\omega_{1,2}$) to cover its radial width (where the radial width is equivalent to $R_{\text{rt}}$ of \eqref{eq_DF_phErr}) and coefficient sets ($\vecnot{\alpha}_{m,i},\vecnot{\beta}_{m,i} \ \forall\ m=0\dots{}M-1, i=1,2$), which cover the zone's angular diameter which is equivalent to determining the desired beamwidth via setting the proper $\kappa$ of \eqref{eqn_H_DF_CB}.
\par
Leaving aside the needed computational effort and physical limitations of transmitting multiple narrowband signals, assuming large $M$ values, we have a super-positioned feedback beamformer which simultaneously scans the entire arena.

>>>>

In modern RADAR related systems, the waveform of choice is pulse based and modulated by CW, or linear/nonlinear frequency scans.
It holds some obvious advantages over the CW transmission such as
\begin{itemize}
    \item Lower power consumption due to lower transmissions duty cycle. 
    \item The use of wide band signals increases spatial resolution in the radial axis.
\end{itemize}
Another interesting option is using several (possibly many) independent harmonics as super positioned multiple dual frequency beamformers, which simultaneously scan a wide area with multiple resolutions.
By merely selecting harmonic couples and filter coefficients, each harmonics pair is pointed to a specific area.
It follows that with the expense of computational effort (without adding elements to the array), it seems possible that one may have simultaneous scan of the entire arena in any wanted direction/range/resolution.
\par 
As a simple example, consider that the arena consists of $M$ zones of interest, where each zone may be described as a angular bounded radial slice (similar to the visualization of Fig.~\ref{fig_rangeAzimuthSelectivity}) which may be described as $$a_{m}=\cBrace{\vecnot{p}\ \middle\vert\  \theta_{d,m,\text{min}}<\text{DOA}\rBrace{\vecnot{p}}<\theta_{d,m,\text{max}}\ ,\ R_{m,\text{min}}<\norm{\vecnot{p}}<R_{m,\text{max}}}\ \forall\ m=0\dots{}M-1.$$
\par
Each zone will be assigned with matching couple of carrier frequencies ($\omega_{1,2}$) to cover its radial width (where the radial width is equivalent to $R_{\text{rt}}$ of \eqref{eq_DF_phErr}) and coefficient sets ($\vecnot{\alpha}_{m,i},\vecnot{\beta}_{m,i} \ \forall\ m=0\dots{}M-1, i=1,2$), which cover the zone's angular diameter which is equivalent to determining the desired beamwidth via setting the proper $\kappa$ of \eqref{eqn_H_DF_CB}.
\par
Leaving aside the needed computational effort and physical limitations of transmitting multiple narrowband signals, assuming large $M$ values, we have a super-positioned FB which simultaneously scans the entire arena.
